Thermodynamic response functions in a cell fluid model

### 2024-08-07 main_morse_response_functions.tex
add numerical values for coefficients alpha, gamma, n_0
add new figures to the text

%\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
%\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references

@@

%**************
%<<<<<<< HEAD
\usepackage[pdftex]{graphicx}
\usepackage{amsmath}    % for "\eqref" macro
%=======
\usepackage{graphicx}
%>>>>>>> 3a31f0b6bd43223c1786eb91b76133393bfa7c2a
%**************

@@

	\subsection{Isothermal compressibility}
	The isothermal compressibility is defined by
	\begin{equation}
		\label{def:isotherm_compres}
		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_T
	\end{equation}

@@

	\subsection{Thermal pressure coefficient}
	The thermal pressure coefficient is defined by
	\begin{equation}
		\label{def:therm_pres_coef}
		\beta_V = \left( \frac{\partial P}{\partial T} \right)_V
	\end{equation}

	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f3.pdf}
		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig3}
	\end{figure}

	\subsection{Thermal expansion coefficient}
	The thermal expansion coefficient is defined by
	\begin{equation}
		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_P
	\end{equation}

	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f4.pdf}
		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of reduced temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig4}
	\end{figure}

>>>>

\usepackage{orcidlink} % to insert a hyperlinked ORCiD logo
\usepackage{amssymb}
\usepackage{physics}
\usepackage{cite} % may be useful for different formats of numerical citation
\usepackage{hyperref} % for hyperlinks in references

@@

%**************
%\usepackage[pdftex]{graphicx}
%\usepackage{amsmath}    % for "\eqref" macro
\usepackage{graphicx}
%**************

@@

	\subsection{Isothermal compressibility}
	The isothermal compressibility is defined by
	\begin{equation}
		\label{def:isotherm_compres}
		K_T = -\frac{1}{V}\left(\frac{\partial V}{\partial P}\right)_{T,<N>}
	\end{equation}

@@

	\subsection{Thermal pressure coefficient}
	The thermal pressure coefficient is defined by
	\begin{equation}
		\label{def:therm_pres_coef}
		\beta_V = \left( \frac{\partial P}{\partial T} \right)_{V,<N>}
	\end{equation}

	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f3a.pdf}
		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig3a}
	\end{figure}
	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f3b.pdf}
		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the effective chemical potential $M$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig3b}
	\end{figure}
	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f3c.pdf}
		\vskip-3mm\caption{The thermal pressure coefficient $\beta_V$ as a function of the relative temperature $\tau$ at different values of the density $\eta$. 
		}\label{fig3c}
	\end{figure}

	\subsection{Thermal expansion coefficient}
	The thermal expansion coefficient is defined by
	\begin{equation}
		\alpha_P = \frac{1}{V}\left(\frac{\partial V}{\partial T}\right)_{P,<N>}
	\end{equation}

	\begin{figure}[h!]
		\centering \includegraphics[width=0.5\textwidth]{f4a.pdf}
		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the density $\bar n$ at different values of relative temperature $\tau > 0$ ($T > T_c$). 
		}\label{fig4a}
	\end{figure}

		\begin{figure}[h!]
		\centering \includegraphics[width=0.45\textwidth]{f4b.pdf}
		\includegraphics[width=0.475\textwidth]{f4c.pdf}
		\vskip-3mm\caption{The thermal expansion coefficient $\alpha_P$ as a function of the effective chemical potential $M$ for different temperatures $\tau = (T - T_c)/T_c$ at $T > T_c$. The two figures differ in the scale of $M$. The left-hand-side figure covers a wider range of $M$, while the right-hand-side one focuses on a range of $M$ around its critical value $0$.
		}\label{fig4b}
	\end{figure}

	\newpage
